---
title: 'MKTG6310-090 Su2019 Assignment 2 Segmenting for a Social Entertainment App v2'
author: "Lynd Bacon, lynd.bacon@hsc.utah.edu"
output:
  html_notebook:
    toc: yes
  pdf_document:
    toc: no
  html_document:
    toc: yes
---

Creative Commons CC by 4.0 Lynd Bacon & Associates, Ltd.  Not warranteed to be suitable for any particular purpose. (You're on your own!)

---

_Ready everything that follows **carefully**_. 

**Set Ups?**

This chunk makes the default directory for a markdown or notebook the same as for the project directory that either one is in.  You may or may not need it, depending on whether you are going to execute anything from this markdown document.
```{r setup} 
#
# knitr::opts_knit$set(root.dir = rprojroot::find_rstudio_root_file())
# 
```

## Introduction

Many organizations collect data from their customers and stakeholders to understand their perceptions and preferences.  A venerable business adage is "Know Your Customers," or "KYC" for short.

The App Happy Company wants to better understand what they believe is the market for a new social entertainment app.  They are currently in the business of providing B2B analytic apps, and they don't yet have a product in the consumer entertainment app category.  A "social entertainment app" is a smart phone or tablet application that  a customer can use to consume media, and to share media content and their opinions about it with people they know.

App Happy hired the Consumer Spy Corporation (CSC) to survey consumers in the market of interest.  CSC collected data from a sample of consumers, and provided App Happy with a dataset of their responses.  The survey questionnaire (see the data dictionary in the file _apphappy-survey-questionnaire-dictionary-2019.pdf_) was based on preliminary qualitative research that included focus groups and one-on-one interviews.  The data collected by CSC are in the R data file _appHappyData-2019.RData_.

## Your Assignment 2 Objective

Help App Happy get to know the potential customers for its app, better.

App Happy needs you to inform their new product strategy and tactics by developing and describing market segments. You'll do this by performing two types of segmentation analysis:  _descriptive post hoc segmentation analysis_, and _predictive post hoc segmentation analysis_.  You'll also help them to better understand which respondents are using only free apps by predicting it using demographic variables.

For your descriptive segmentation analysis, you'll use _one_ of two approaches, a partitioning clustering method (k-means), or a hierarchical clustering method.  You'll use finite mixture regression, also called clusterwise regression, or latent class regression, for the predictive segmentation analysis.  In the case of each kind of analysis you'll profile (describe) the segments you identify, and you'll interpret your results for App Happy.  You'll apply either a binary logistic regression model or a binary probit regression model to predct the use of only free apps.

Do your work using R, and assemble it in an R Notebook.  Submit both your Notebook (.Rmd) and a pdf version of it on Canvas. Details follow.

## What To Do

### Part 1: Load the Data, Munge It, Do Some EDA

__Two data.frames in one__. Load the RData file into R.  In it you'll find two data.frames.  Both have the same variables, but one has numeric codes for the survey responses, and the other has the _character strings_ that labelled the response alternatives in the questionnaire.  

For example, for q48, which is about the highest level of education attained, the numeric data will have numeric codes from 1 to 6 (if they are all correct codes), while the character data will have values like "Some college" and "High school graduate."  The numeric data are what you should analyze.  The character data can help in understanding the numeric data.

```{r load myData, include=FALSE}
load("./appHappyData-2019.RData")
appHappyLabs <- apphappy.4.labs.frame
appHappyNums <- apphappy.4.num.frame
```

```{r}
head(appHappyLabs,10)
head(appHappyNums,10)
```

```{r}

```


Do an exploratory analysis of App Happy's data, paying particular attention to the variables you'll use in the analyses described below. "EDA" is the usual preliminary, important step in any analysis effort. Note in particular any missing values, anomalous codes, and so on.

```{r}
naCounts <- appHappyNums %>% is.na %>% colSums
naCounts
cat('\n')
naCounts[naCounts>0]
```

```{r}
cat('Number of records (rows, observations):\n')
nrow(appHappyLabs)
cat('Number of variables:\n')
ncol(appHappyLabs)
cat('Different kinds of variables (data types):\n')
unique(sapply(appHappyLabs, typeof))
```

### Part 2: Post Hoc Descriptive Segmentation Analysis and Profiling  

App Happy wants to segment the market based on customers' _attitudes_.   Questionnaire items q24, q25, and q26 measure various attitudes.  These items were measured using a rating scale called a _Likert_ scale. Note any items that have either very little or relatively large variation.  Also summarize the correlations between these items.  A useful thing to do is to reverse the numerical labels of these items so that larger numbers indicate greater agreement. (People tend to think that larger numbers mean more of something. )

For your segmentation analysis, do your clustering using the data for the the twelve (12) _attitudinal_ measures in the *q24* question set. Use _one of_ a k-means clustering method,  or a tree-based method hierarchical clustering, to define customer segments.  (You decide which to use.) Use your "best" clustering solution to identify market segments for App Happy. (Your "best" solution is the one with clusters that are well separated, and that lends itself most easily to interpretation.) Describe how each segment uniquely differs from the other segments, and what these differences suggest for App Happy's plan to market the app it is considering.

### Part 3: Probability of Using Only Free Apps

App Happy wants you to estimate models that predict whether a respondent _only_ uses free apps. This is indicated by the data of variable q12. Create a new binary dependent variable called `onlyFreeApps` that has a value of 1 if the value of variable q12 equals 6, and is 0 if q12 equals 1,2,3,4 or 5. Be sure to take into account any missing data or incorrectly coded values.   _Randomly_ split the data into a model estimation sample and a model test sample, 80% estimation, and 20% test.  Use the estimation sample to estimate _either_ a binary logistic regression model, _or_ a binary probit regression model. For either type of model, use the _demographic_ variables in the survey data as predictor variables.  These are variables q1, and q48 through q57, but omit variable q54. (Why might a company omit q54 from its analyses?)

For the best of the type of model you chose to use, calculate its _predictive accuracy_ in terms of percent correct prediction of responses, for both the estimation data and for the test data.  (Question: what do differences between the two tell you about your model?).  

Your "best" model should only include predictors that are statistically significant at the conventional level, a Type I error rate of 0.05, and whose accuracy doesn't decrease much (or at all) when it is used to predict `onlyFreeApps` using the held out, 20% test data.

Interpret your best model's results for App Happy.  Mention any assumptions that you think might be important to for Appy Happy to consider when interpreting your model's results.

### Part 4: Post Hoc Predictive Segmentation Analysis

App Happy wants to know if potential customers differ in terms of how their attitudes predict the likelihood of paying for apps. The question is, are there customer segments that differ in terms of how their attitudes predict whether they pay for apps or not?

Estimate binary logit finite mixture models to predict 1 minus `onlyFreeApps` to identify the one that best describes the data. Profile these segments, and describe how each segment uniquely differs from the other segments, and what these differences suggest for App Happy's plan to market it's app.

## How To Do It

### R Packages and Functions That You Are Likely to Be Useful 

For _descriptive segmentation cluster analysis_, you'll probably find the following useful: kmeans(), hclust(), cutree(), NbClust().  Profiling segments is about summarizing differences between them.  You'll want to use tables and tests of mean differences for doing it, depending on the kind of data you're working with, of course.

For _predicting the use of only free apps_, you'll find the glm() function for estimating logistic or probit regression models to be handy.

For _predictive segmentation analysis_, the `mclust` and the `flexmix` packages can be used to do this analysis.  Both do finite mixture regresssion or classification.  This kind of regression is sometimes called "clusterwise" regression.  You'll note from the CRAN task view that there are also Bayesian methods for doing this sort of mixture regression.

### Reproducible Marketing Data Science Assignment Work Product  

Assemble your work in an R Notebook.  Organize your Notebook so that it effectively shows and explains what you did, and what you found, to other persons who might want to replicate your work.  It should exemplify good reproducible data science practice.  Don't exceed **16** (_16_) pages in length in your pdf document.  Staying within this limit may require you to decide what's important to include in your report, and what can be gotten rid of. A design principle is to "keep what's essential, and get rid of the rest."  Include what's important for a reader to understand your story.  Don't be WET ('waste everyone's time') by including content that's unimportant or irrelavant.

Be sure to address every question or objective of this assignment.

Note that your Notebook may be shared with other teams in this class for discussion purposes.

IMPORTANT: Just one member of your team should upload your work on this assignment to Canvas.  Both your R Notebook and a pdf version produced from it should be submitted.  Include at the beginning of what you turn in the name of your assignment team (e.g. assignment team 2), and the names of your team members. 

Last but not least, be sure to post questions (as well as suggestions for your classmates) to the Assignment 2 Huddle.

### When To Do It By

The submission date is indicated on Canvas.  Try not to be late!

